Type cones of $\b{g}$-vector fans

### 2019-04-01 thirdPaper/draft/typeConeAssociahedra.tex
improvements + table

%We now extend the results of the previous section to the $\b{g}$-vector fan of any finite type cluster algebra with respect to any seed (acyclic or not).
Cluster algebras were introduced by S.~Fomin and A.~Zelevinsky~\cite{FominZelevinsky-ClusterAlgebrasI} with motivation coming from total positivity and canonical bases.
Here, we will focus on finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasII} and more specifically on properties of their $\b{g}$-vectors~\cite{FominZelevinsky-ClusterAlgebrasIV}.
These $\b{g}$-vectors support a complete simplicial fan, which is known to be the normal fan of a polytope called generalized associahedron. These polytopal realizations were first constructed for bipartite initial seeds by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} using the $\b{d}$-vector fans of~\cite{FominZelevinsky-YSystems}, then for acyclic initial seeds by C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} using Cambrian lattices and fans of N.~Reading and D.~Speyer~\cite{Reading-CambrianLattices, ReadingSpeyer}, and revisited by S.~Stella~\cite{Stella}, and by V.~Pilaud and C.~Stump~\cite{PilaudStump-brickPolytope} via brick polytopes, and finally for arbitrary initial seeds by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella}.
More recently in~\cite{BazierMatteDouvilleMousavandThomasYildirim}, V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim extended the construction of associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to acyclic seeds of simply laced finite type cluster algebras.
Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply laced or not) cluster algebra with respect to any seed (acyclic or not) by providing a direct proof that the type cone of the $\b{g}$-vector fan of any finite type cluster algebra is simplicial.

\subsubsection{Cluster algebras and $\b{g}$-vector fans}

We present some definitions and properties of finite type cluster algebras and their $\b{g}$-vector fans, following the presentation of~\cite{HohlwegPilaudStella}.

@@

\para{The $\b{g}$-vector fan and generalized associahedron}
%
The following statement is well known and admits several possible proofs as discussed in~\cite[Sect.~4]{HohlwegPilaudStella}.
Examples are illustrated in \cref{fig:clusterFans}.

\begin{figure}[h]
	\capstart
	%\centerline{\includegraphics[scale=.45]{clusterFans}}
	\centerline{
	\begin{overpic}[scale=.45]{clusterFans}
	\put(-19,30){$\left[\begin{array}{@{}c@{\;}c@{\;}c@{}} 0 & -1 & 1 \\ 1 & 0 & -1 \\ -1 & 1 & 0 \end{array}\right]$}
	\put(98,30){$\left[\begin{array}{@{}c@{\;}c@{\;}c@{}} 0 & -1 & 2 \\ 1 & 0 & -2 \\ -1 & 1 & 0 \end{array}\right]$}
	\end{overpic}
	}
	\caption{Two $\b{g}$-vector fans~$\gvectorFan[\B_\circ]$ for the type~$A_3$~(left) and type~$C_3$~(right) cyclic initial exchange matrices. As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$. Illustration from~\cite{HohlwegPilaudStella}.}
	\label{fig:clusterFans}
\end{figure}

\begin{theorem}
\label{thm:gvectorFanCA}
For any finite type exchange matrix~$\B_\circ$, the collection of cones \\[.1cm]
\centerline{
$\gvectorFan[\B_\circ] \eqdef \bigset{\R_{\ge0} \, \gvectorsFull{\B_\circ}{\seed}}{\seed \text{ seed of } \principalClusterAlgebra},$
} \\[.1cm]
together with all their faces, forms a complete simplicial fan, called the \defn{$\b{g}$-vector fan} of~$\B_\circ$.
\end{theorem}

@@

\begin{theorem}[{\cite[Thm.~26]{HohlwegPilaudStella}}]
\label{thm:generalizedAsso}
For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is the normal fan of the \defn{$\B_\circ$-associahedron}~$\Asso[\B_\circ, \b{h}]$ defined equivalently as
\begin{enumerate}[(i)]
\item the convex hull of the points~$\sum_{x \in \seed} \b{h}_x \, \cvectorFull{\B_\circ^\vee}{\seed^\vee}{x^\vee}$ for all seeds~$\seed$ of~$\principalClusterAlgebra$, or
\item the intersection of the halfspaces~$\set{\b{v} \in V^\vee}{\dotprod{\gvectorFull{\B_\circ}{x}}{\b{v}} \le \b{h}_x}$ for all cluster variables~$x$ of~$\principalClusterAlgebra$.
\end{enumerate}
\end{theorem}

\para{Mutations in the $\b{g}$-vector fan}
%
We now discuss the linear dependences between $\b{g}$-vectors of adjacent seeds.
The following proposition was stated in~\cite[Lem.~19]{HohlwegPilaudStella}.

@@

Note that \cref{lem:linearDependencegvectorsCA} implies \cref{thm:generalizedAsso} since it ensures that the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the $\b{g}$-vector fan contains the cone of~${\b{h} \in \R^{\principalVariables}}$ such that
\(
\b{h}_x + \b{h}_{x'} > \sum_{{y \in \cluster \cap \cluster', \; b_{xy} < 0}} -b_{xy}
\)
and
\(
\b{h}_x + \b{h}_{x'} > \sum_{{y \in \cluster \cap \cluster', \; b_{xy} > 0}} b_{xy} \, \b{h}_y
\)
for any seeds~$(\B, \cluster)$ and~$(\B', \cluster')$ with~${\cluster \ssm \{x\} = \cluster' \ssm \{x'\}}$.

@@

\begin{proposition}
\label{prop:uniqueExchangePropertyCA}
For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan has the unique exchange relation property.
\end{proposition}

\subsubsection{Type cone of finite type $\b{g}$-vector fans}

The linear dependences of \cref{lem:linearDependencegvectorsCA} provide a redundant description of the type cone of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
We denote by~$\b{n}(\B_\circ, x, x')$ the normal vector of the inequality of the type cone corresponding to two exchangeable cluster variable~$x$ to~$x'$ (it is well defined by \cref{prop:uniqueExchangePropertyCA}).
In other words, depending on which of the two linear dependences of \cref{lem:linearDependencegvectorsCA} holds, we have
\[
\b{n}(\B_\circ, x, x') \eqdef \b{f}_x + \b{f}_{x'} - \sum_{\substack{y \in \cluster \cap \cluster' \\ b_{xy} < 0}} -b_{xy} \, \b{f}_y
\qquad\text{or}\qquad
\b{n}(\B_\circ, x, x') \eqdef \b{f}_x + \b{f}_{x'} - \sum_{\substack{y \in \cluster \cap \cluster' \\ b_{xy} > 0}} b_{xy} \, \b{f}_y,
\]
where~$(\b{f}_x)_{x \in \principalVariables}$ denotes the canonical basis of~$\R^{\principalVariables}$.
We obtain the following statement.

\begin{corollary}
\label{coro:typeConeCA}
For any finite type exchange matrix~$\B_\circ$, the type cone of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is given by
\[
\typeCone(\gvectorFan[\B_\circ]) = \set{\b{h} \in \R^{\principalVariables}}{\dotprod{\b{n}(\B_\circ, x, x')}{\b{h}} > 0 \text{ for all exchangeable cluster variables } x, x'}.
\]
\end{corollary}

\begin{example}
%sage: B = Matrix([[0,-1,1],[1,0,-1],[-1,1,0]])
%sage: CA = ClusterAlgebra(B)
%
%sage: CA.explore_to_depth(infinity)
%sage: gvectors = CA.cluster_fan().rays()
%sage: for gvector in gvectors:
%....:     print gvector, CA.cluster_variable(gvector)
%....:     
%N(1, 0, 0) x0
%N(0, 0, 1) x2
%N(1, -1, 0) (x0 + x2)/x1
%N(0, 0, -1) (x0 + x1 + x2)/(x1*x2)
%N(-1, 0, 1) (x1 + x2)/x0
%N(0, -1, 0) (x0 + x1 + x2)/(x0*x1)
%N(-1, 0, 0) (x0 + x1 + x2)/(x0*x2)
%N(0, 1, 0) x1
%N(0, 1, -1) (x0 + x1)/x2
%
%sage: TCCA = type_cone_CA(CA)
%sage: TCCA
%A 9-dimensional polyhedron in QQ^9 defined as the convex hull of 1 vertex, 6 rays, 3 lines
%sage: TCCA.inequalities()
%(An inequality (-1, 0, 1, -1, 0, 0, 0, 0, 1) x + 0 >= 0,
% An inequality (1, 0, -1, 0, 0, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, -1, 1, 0, 1, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 1, 0, 0, -1, 0, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 1, 0, 0, 0, 1, -1) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 1, 0, -1, -1, 1) x + 0 >= 0)

@@

\begin{proposition}
\label{prop:extremalExchangeablePairsCA}
For any finite type exchange matrix~$\B_\circ$ (acyclic or not), the non-initial mesh mutations precisely correspond to the extremal exchangeable pairs of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
\end{proposition}

@@

Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeCA,prop:extremalExchangeablePairsCA}, we derive the following description of all polytopal realizations of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
This result was stated in~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the special situation of acyclic seeds in simply-laced types.
Note that our proof is quite different from~\cite{BazierMatteDouvilleMousavandThomasYildirim} as it relies on our type cone approach.

\begin{theorem}
For any finite type exchange matrix~$\B_\circ$, and for any~$\b{\ell} \in \R_{>0}^{\meshes}$, the polytope
\[
R_{\b{\ell}}(\B_\circ) \eqdef \Bigset{\b{z} \in \R^{\principalVariables}}{\b{z} \ge 0 \text{ and } \b{z}_x + \b{z}_{x'} = \sum_{y \in \principalVariables} \alpha_{x,x',y} \, \b{z}_{y} \text{ for all } (x,x') \in \meshes}
\]
is a generalized associahedron, whose normal fan is the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
\end{theorem}

@@

\begin{example}
\label{exm:typeConeNKC}
Consider the gentle quivers of \cref{fig:nonkissingFans}.
%sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e3':['b']}}, [('a','b')])
%
%sage: Q.non_kissing_fan().rays()
%N( 1,  0,  0),
%N( 0,  0,  1),
%N( 1, -1,  0),
%N( 0,  0, -1),
%N( 0, -1,  0),
%N(-1,  0,  0),
%N( 0,  1,  0),
%N( 0,  1, -1)
%in 3-d lattice N
%
%sage: TCNKC = type_cone_NKC(Q)
%sage: TCNKC
%A 8-dimensional polyhedron in QQ^8 defined as the convex hull of 1 vertex, 5 rays, 3 lines
%sage: TCNKC.inequalities()
%(An inequality (-1, 0, 1, -1, 0, 0, 0, 1) x + 0 >= 0,
% An inequality (1, 0, -1, 0, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 1, 0, 0, 0, 0, -1, 1) x + 0 >= 0,
% An inequality (0, 0, 1, 0, -1, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 1, 0, 0, 1, -1) x + 0 >= 0)
%sage: TCNKC.lines()
%(A line in the direction (0, 0, 1, 0, 1, 0, -1, -1),
% A line in the direction (1, 0, 0, 0, -1, -1, 1, 1),
% A line in the direction (0, 1, 0, -1, 0, 0, 0, -1))

>>>>

%We now extend the results of the previous section to the $\b{g}$-vector fan of any finite type cluster algebra with respect to any seed (acyclic or not).
Cluster algebras were introduced by S.~Fomin and A.~Zelevinsky~\cite{FominZelevinsky-ClusterAlgebrasI} with motivation coming from total positivity and canonical bases.
Here, we will focus on finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasII} and more specifically on properties of their $\b{g}$-vectors~\cite{FominZelevinsky-ClusterAlgebrasIV}.
These $\b{g}$-vectors support a complete simplicial fan, which is called \defn{$\b{g}$-vector fan} or \defn{cluster fan}. It is known to be the normal fan of a polytope called generalized associahedron. These polytopal realizations were first constructed for bipartite initial seeds by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} using the $\b{d}$-vector fans of~\cite{FominZelevinsky-YSystems}, then for acyclic initial seeds by C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} using Cambrian lattices and fans of N.~Reading and D.~Speyer~\cite{Reading-CambrianLattices, ReadingSpeyer}, and revisited by S.~Stella~\cite{Stella}, and by V.~Pilaud and C.~Stump~\cite{PilaudStump-brickPolytope} via brick polytopes, and finally for arbitrary initial seeds by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella}.
More recently in~\cite{BazierMatteDouvilleMousavandThomasYildirim}, V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim extended the construction of associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to acyclic seeds of simply laced finite type cluster algebras.
Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply laced or not) cluster algebra with respect to any seed (acyclic or not) by providing a direct proof that the type cone of the cluster fan of any finite type cluster algebra is simplicial.

\subsubsection{Cluster algebras and cluster fans}

We present some definitions and properties of finite type cluster algebras and their cluster fans, following the presentation of~\cite{HohlwegPilaudStella}.

@@

\para{Cluster fan and generalized associahedron}
%
The following statement is well known and admits several possible proofs as discussed in~\cite[Sect.~4]{HohlwegPilaudStella}.
Examples are illustrated in \cref{fig:clusterFans}.

\begin{figure}[h]
	\capstart
	%\centerline{\includegraphics[scale=.45]{clusterFans}}
	\centerline{
	\begin{overpic}[scale=.45]{clusterFans}
	\put(-19,30){$\left[\begin{array}{@{}c@{\;}c@{\;}c@{}} 0 & -1 & 1 \\ 1 & 0 & -1 \\ -1 & 1 & 0 \end{array}\right]$}
	\put(98,30){$\left[\begin{array}{@{}c@{\;}c@{\;}c@{}} 0 & -1 & 2 \\ 1 & 0 & -2 \\ -1 & 1 & 0 \end{array}\right]$}
	\end{overpic}
	}
	\caption{Two cluster fans~$\gvectorFan[\B_\circ]$ for the type~$A_3$~(left) and type~$C_3$~(right) cyclic initial exchange matrices. As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$. Illustration from~\cite{HohlwegPilaudStella}.}
	\label{fig:clusterFans}
\end{figure}

\begin{theorem}
\label{thm:gvectorFanCA}
For any finite type exchange matrix~$\B_\circ$, the collection of cones \\[.1cm]
\centerline{
$\gvectorFan[\B_\circ] \eqdef \bigset{\R_{\ge0} \, \gvectorsFull{\B_\circ}{\seed}}{\seed \text{ seed of } \principalClusterAlgebra},$
} \\[.1cm]
together with all their faces, forms a complete simplicial fan, called the \defn{$\b{g}$-vector fan} or \defn{cluster fan} of~$\B_\circ$.
\end{theorem}

@@

\begin{theorem}[{\cite[Thm.~26]{HohlwegPilaudStella}}]
\label{thm:generalizedAsso}
For any finite type exchange matrix~$\B_\circ$, the cluster fan~$\gvectorFan[\B_\circ]$ is the normal fan of the \defn{$\B_\circ$-associahedron}~$\Asso[\B_\circ, \b{h}]$ defined equivalently as
\begin{enumerate}[(i)]
\item the convex hull of the points~$\sum_{x \in \seed} \b{h}_x \, \cvectorFull{\B_\circ^\vee}{\seed^\vee}{x^\vee}$ for all seeds~$\seed$ of~$\principalClusterAlgebra$, or
\item the intersection of the halfspaces~$\set{\b{v} \in V^\vee}{\dotprod{\gvectorFull{\B_\circ}{x}}{\b{v}} \le \b{h}_x}$ for all cluster variables~$x$ of~$\principalClusterAlgebra$.
\end{enumerate}
\end{theorem}

\para{Mutations in the cluster fan}
%
We now discuss the linear dependences between $\b{g}$-vectors of adjacent seeds.
The following proposition was stated in~\cite[Lem.~19]{HohlwegPilaudStella}.

@@

Note that \cref{lem:linearDependencegvectorsCA} implies \cref{thm:generalizedAsso} since it ensures that the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the cluster fan contains the cone of~${\b{h} \in \R^{\principalVariables}}$ such that
\(
\b{h}_x + \b{h}_{x'} > \sum_{{y \in \cluster \cap \cluster', \; b_{xy} < 0}} -b_{xy}
\)
and
\(
\b{h}_x + \b{h}_{x'} > \sum_{{y \in \cluster \cap \cluster', \; b_{xy} > 0}} b_{xy} \, \b{h}_y
\)
for any seeds~$(\B, \cluster)$ and~$(\B', \cluster')$ with~${\cluster \ssm \{x\} = \cluster' \ssm \{x'\}}$.

@@

\begin{proposition}
\label{prop:uniqueExchangePropertyCA}
For any finite type exchange matrix~$\B_\circ$, the cluster fan has the unique exchange relation property.
\end{proposition}

\subsubsection{Type cone of finite type cluster fans}

The linear dependences of \cref{lem:linearDependencegvectorsCA} provide a redundant description of the type cone of the cluster fan~$\gvectorFan[\B_\circ]$.
We denote by~$\b{n}(\B_\circ, x, x')$ the normal vector of the inequality of the type cone corresponding to two exchangeable cluster variable~$x$ to~$x'$ (it is well defined by \cref{prop:uniqueExchangePropertyCA}).
In other words, depending on which of the two linear dependences of \cref{lem:linearDependencegvectorsCA} holds, we have
\[
\b{n}(\B_\circ, x, x') \eqdef \b{f}_x + \b{f}_{x'} - \sum_{\substack{y \in \cluster \cap \cluster' \\ b_{xy} < 0}} -b_{xy} \, \b{f}_y
\qquad\text{or}\qquad
\b{n}(\B_\circ, x, x') \eqdef \b{f}_x + \b{f}_{x'} - \sum_{\substack{y \in \cluster \cap \cluster' \\ b_{xy} > 0}} b_{xy} \, \b{f}_y,
\]
where~$(\b{f}_x)_{x \in \principalVariables}$ denotes the canonical basis of~$\R^{\principalVariables}$.
We obtain the following statement.

\begin{corollary}
\label{coro:typeConeCA}
For any finite type exchange matrix~$\B_\circ$, the type cone of the cluster fan~$\gvectorFan[\B_\circ]$ is given by
\[
\typeCone(\gvectorFan[\B_\circ]) = \set{\b{h} \in \R^{\principalVariables}}{\dotprod{\b{n}(\B_\circ, x, x')}{\b{h}} > 0 \text{ for all exchangeable cluster variables } x, x'}.
\]
\end{corollary}

\begin{example}
Consider the initial $B$-matrices~$\B_\circ$ whose cluster fans are illustrated in \cref{fig:clusterFans}.
\newcommand{\compactVector}[3]{\begin{bmatrix} #1 \\[-.1cm] #2 \\[-.1cm] #3 \end{bmatrix}}

\[
\begin{array}{c|ccccccccc}
\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1 + x_2}{x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} \\[.3cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{0}{0}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} \\[.5cm]
\text{lines}		& 0 & 0 & 1 & 1 & 0 & -1 & -1 & 0 & 0 \\
					& 0 & -1 & 0 & 0 & 1 & -1 & 0 & 0 & 1 \\
					& 1 & 1 & 0 & -1 & 0 & 1 & 0 & -1 & -1 \\[.2cm]
\text{inequalities} & -1 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 \\
 					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
 					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
 					& 0 & 0 & 1 & -1 & 0 & 0 & 0 & 1 & 0 \\
 					& 0 & 1 & 0 & 0 & 0 & -1 & 1 & 0 & 0 \\
 					& 0 & -1 & 0 & 1 & 0 & 1 & 0 & -1 & 0
\end{array}
\]

%sage: B = Matrix([[0,-1,1],[1,0,-1],[-1,1,0]])
%sage: CA = ClusterAlgebra(B)
%
%sage: CA.explore_to_depth(infinity)
%sage: gvectors = CA.cluster_fan().rays()
%sage: for gvector in gvectors:
%....:     print gvector, CA.cluster_variable(gvector)
%....:     
%N(1, 0, 0) x0
%N(0, 0, 1) x2
%N(1, -1, 0) (x0 + x2)/x1
%N(0, 0, -1) (x0 + x1 + x2)/(x1*x2)
%N(-1, 0, 1) (x1 + x2)/x0
%N(0, -1, 0) (x0 + x1 + x2)/(x0*x1)
%N(-1, 0, 0) (x0 + x1 + x2)/(x0*x2)
%N(0, 1, 0) x1
%N(0, 1, -1) (x0 + x1)/x2
%
%sage: TCCA = type_cone_CA(CA)
%sage: TCCA
%A 9-dimensional polyhedron in QQ^9 defined as the convex hull of 1 vertex, 6 rays, 3 lines
%sage: TCCA.lines()
%(A line in the direction (0, 1, 0, -1, 1, 0, 0, 0, -1),
% A line in the direction (0, 0, 1, 0, 0, 1, 0, -1, -1),
% A line in the direction (1, 0, 0, 0, -1, -1, -1, 1, 1))
%sage: TCCA.inequalities()
%(An inequality (-1, 0, 1, -1, 0, 0, 0, 0, 1) x + 0 >= 0,
% An inequality (1, 0, -1, 0, 0, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, -1, 1, 0, 1, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 1, 0, 0, -1, 0, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 1, 0, 0, 0, 1, -1) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 1, 0, -1, -1, 1) x + 0 >= 0)

\centerline{$
\begin{array}{c|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{}c@{}c@{}c}
\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2}{x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}$} \\[.3cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{2}{-1} & \compactVector{0}{1}{-1} & \compactVector{-1}{1}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} & \compactVector{-2}{0}{1} & \compactVector{-1}{0}{0}  \\[.5cm]
\text{lines}		& 1 & 1 & 2 & 1 & 0 & 0 & -1 & 0 & -1 & -2 & 0 & -1 \\
					& 0 & 1 & 0 & 0 & -1 & 2 & 1 & 1 & -1 & 0 & 0 & 0 \\
					& 0 & 0 & -1 & -1 & 0 & 1 & 1 & 0 & 0 & 1 & -1 & 0 \\[.2cm]
\text{inequalities} & 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 \\
					& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
					& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 \\
					& -1 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & -1 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 \\
					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
					& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0
\end{array}
$}

@@

\begin{proposition}
\label{prop:extremalExchangeablePairsCA}
For any finite type exchange matrix~$\B_\circ$ (acyclic or not), the non-initial mesh mutations precisely correspond to the extremal exchangeable pairs of the cluster fan~$\gvectorFan[\B_\circ]$.
\end{proposition}

@@

Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeCA,prop:extremalExchangeablePairsCA}, we derive the following description of all polytopal realizations of the cluster fan~$\gvectorFan[\B_\circ]$.
This result was stated in~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the special situation of acyclic seeds in simply-laced types.
Note that our proof is quite different from~\cite{BazierMatteDouvilleMousavandThomasYildirim} as it relies on our type cone approach.

\begin{theorem}
For any finite type exchange matrix~$\B_\circ$, and for any~$\b{\ell} \in \R_{>0}^{\meshes}$, the polytope
\[
R_{\b{\ell}}(\B_\circ) \eqdef \Bigset{\b{z} \in \R^{\principalVariables}}{\b{z} \ge 0 \text{ and } \b{z}_x + \b{z}_{x'} = \sum_{y \in \principalVariables} \alpha_{x,x',y} \, \b{z}_{y} \text{ for all } (x,x') \in \meshes}
\]
is a generalized associahedron, whose normal fan is the cluster fan~$\gvectorFan[\B_\circ]$.
\end{theorem}

@@

\begin{example}
\label{exm:typeConeNKC}
Consider the gentle quivers whose non-kissing fans are illustrated in \cref{fig:nonkissingFans}.
%sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e3':['b']}}, [('a','b')])
%
%sage: Q.non_kissing_fan().rays()
%N( 1,  0,  0),
%N( 0,  0,  1),
%N( 1, -1,  0),
%N( 0,  0, -1),
%N( 0, -1,  0),
%N(-1,  0,  0),
%N( 0,  1,  0),
%N( 0,  1, -1)
%in 3-d lattice N
%
%sage: TCNKC = type_cone_NKC(Q)
%sage: TCNKC
%A 8-dimensional polyhedron in QQ^8 defined as the convex hull of 1 vertex, 5 rays, 3 lines
%sage: TCNKC.inequalities()
%(An inequality (-1, 0, 1, -1, 0, 0, 0, 1) x + 0 >= 0,
% An inequality (1, 0, -1, 0, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 1, 0, 0, 0, 0, -1, 1) x + 0 >= 0,
% An inequality (0, 0, 1, 0, -1, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 1, 0, 0, 1, -1) x + 0 >= 0)
%sage: TCNKC.lines()
%(A line in the direction (0, 0, 1, 0, 1, 0, -1, -1),
% A line in the direction (1, 0, 0, 0, -1, -1, 1, 1),
% A line in the direction (0, 1, 0, -1, 0, 0, 0, -1))
